---
title: "Analyse des commentaires Airbnb : extraction des facettes"
author: "Christophe Benavent"
date: today
institute: "Université Dauphine - PSL / DRM / ACSS-PSAI" 
format: 
  beamer: 
    aspectratio: 43
    navigation: horizontal
    theme: CambridgeUS
    colortheme: default
    fig-pos: 'center'
    fig-width: 10
    fig-height: 7
    incremental: true 
header-includes:
  - |
    \definecolor{DeepBlue}{RGB}{10,35,92}
    \definecolor{Bordeaux}{RGB}{125,24,54}
    \setbeamercolor{structure}{fg=DeepBlue}
    \setbeamercolor{palette primary}{bg=DeepBlue,fg=white}
    \setbeamercolor{palette secondary}{bg=Bordeaux,fg=white}
    \setbeamercolor{palette tertiary}{bg=DeepBlue,fg=white}
    \setbeamercolor{frametitle}{fg=DeepBlue}
    \setbeamercolor{title}{fg=Bordeaux}
    \setbeamercolor{alerted text}{fg=Bordeaux}
execute:
  echo: false
  warning: false
  error: false
editor: visual
bibliography: references.bib
---

# General Data

In this task, we first analyze the detection of aspects that emerge in consumer reviews.

We then examine their relationship with the overall sentiment, as measured by two instruments.

```{r}

library(tidyverse)
library(readr)
library(cld3)
library(ggwordcloud)

sentiment_analysis_results <- read_csv("sentiment_analysis_results.csv")


```

------------------------------------------------------------------------

# Aspects extraction

text = text\[:1000\]

prompt = f"""Extract the main aspects (topics/themes) mentioned in this Airbnb review. Return only a comma-separated list of 3-7 key aspects. Be concise and specific. Examples of aspects: cleanliness, location, communication, amenities, noise, comfort, value, host responsiveness, wifi, kitchen, bed quality, etc."""

-   cpu- gemma3:4b - sample 1000 - 1h 20 - 5.11s/item

-   gpu h100 - Mistral32b ? - - - s/item

code python :

------------------------------------------------------------------------

## Aspects

A few general aspects and a bunch of more specific ones.

```{r}

df <- read_csv("aspect_extraction_results.csv") 
  
df_separe <- df %>%
  separate(
    col = Aspects,
    into = paste0("aspect_", 1:7),
    sep = ";",
    fill = "right"
  ) |>
  pivot_longer(-c(Review, Aspect_Count), names_to = "col", values_to = "Aspects") |>
  mutate(Aspects=str_squish(Aspects),
         Aspects=str_to_sentence(Aspects)
         )|>
  filter(!is.na(Aspects))



foo<-df_separe |>
  mutate(Aspects=ifelse(grepl("Host", Aspects),"Host", Aspects),
         Aspects=ifelse(grepl("Family", Aspects),"Family", Aspects),
         Aspects=ifelse(grepl("Neighborhood", Aspects),"Neighborhood", Aspects),
         Aspects=ifelse(grepl("Local", Aspects),"Local", Aspects),
         Aspects=ifelse(grepl("Apartment", Aspects),"Apartment", Aspects)) |> # to be improved...
  group_by(Aspects)|>
  summarise(n=n()) |>
  mutate(n=as.numeric(n))|>
  arrange(desc(n)) |>
  mutate(sum=cumsum(n)) |>
  filter(n>4)

set.seed(42)
ggplot(foo, aes(label = Aspects, size = log(n), color= log(n))) +
  geom_text_wordcloud() +
  scale_size_area(max_size = 10) +
  scale_color_gradient(low = "firebrick2", high = "green4") +  # Dégradé de vert
  theme_minimal()+labs(caption="Size are log proportionnal to frequencies >5 ")


```

## excercise

A worcloud where relative postion of labels reflect their correlations.

compute de distance matrix, project in 2D with tsne or umap.

## 

```{r}

foo1<-df_separe |>
  left_join(foo) |>
  filter(n>20) |>
  select(-col, -Aspect_Count, -n, -sum)|>
  mutate(k=1)|>
  pivot_wider(id_cols = "Review", names_from = "Aspects", values_from ="k") |>
    mutate(across(where(is.numeric), ~ replace_na(., 0)))



df1 <- df |>
  left_join(foo1)

df2 <- cbind(df1,sentiment_analysis_results)
```

------------------------------------------------------------------------

## Sentiment

On examine la convergence de deux modèles de sentiment bertsementiment et ??

------------------------------------------------------------------------

```{r}

ggplot(df2, aes(y=sentiment_score, x = sentiment))+
  geom_violin(aes(fill=sentiment), alpha=.3)+
  scale_fill_ordinal() +
  # Ajouter les points des moyennes
  stat_summary(
    fun = mean,          # Calcule la moyenne
    geom = "point",     # Affiche un point
    shape = 18,         # Forme du point (18 = losange)
    size = 4,           # Taille du point
    color = "firebrick",      # Couleur des points
    fill = "firebrick"        # Remplissage des points
  ) +
  # Ajouter une ligne connectant les moyennes
  stat_summary(
    fun = mean,          # Calcule la moyenne
    geom = "line",       # Trace une ligne
    group = 1,          # Connecte tous les points
    color = "firebrick",       # Couleur de la ligne
    linewidth = 0.8     # Épaisseur de la ligne
  ) +
  # Améliorer la lisibilité
  labs(
    title = "Distribution des scores de sentiment par catégorie",
    x = "Sentiment",
    y = "Score de sentiment"
  )


```

---

## Do  Facets Explain Sentiment?


```{r}

fit<-lm(sentiment_score ~nwords+ Aspect_Count+ langue_short+Comfort+Noise+Location+Quietness+Cleanliness, df2)

summary(fit)

```

## References
